Deep Reinforcement Learning for Conservation Decisions

### 2021-09-30 manuscript/manuscript.Rmd
Changing language on behav eco paragraph but more to do here

<!-- RL for behavioral ecology is not the same as RL for conservation -->
This paper does not set the precedent as the first application of RL to ecology.
There have been a number of studies applying RL to behavioral ecology, typically with multi-agent environments [@wang_reinforcement_2020, @frankenhuis_enriching_2019, @perolat_multi-agent_2017].
Yet, it is important to distinguish the aim of these behavioral studies from the aim of applying RL to conservation management.
In behavioral ecology studies, RL agents are used to represent organisms.
Assuming that animals attempt to maximize some cumulative reward like RL agents, the authors of these studies draw conclusions about animal behavior and evolution by observing how the RL agents perform.
When applying deep RL to conservation management, we do not make the assumption that the behavior of an RL agent is a good substitute for the behavior of an animal.
For conservation management, we instead propose using RL as a tool to search for solutions to decision-making problems.

@@

<!-- Model free is great bc we don't know the true models -->
The rapidly expanding class of model-free RL algorithms is particularly appealing given the ubiquitous presence of model uncertainty in ecological dynamics.
Rarely do we know the underlying functional forms for ecological processes.
Methods which must first assume something about the structure or functional form of a process before estimating the corresponding parameter can only ever be as good as those structural assumptions.
Frequently available ecological data is insufficient to distinguish between possible alternative models [@knape_are_2012], or the correct model may be non-identifiable with any amount of data.
Model-free RL approaches offer a powerful solution for this thorny issue.
Model-free algorithms have proven successful at learning effective policies even when the underlying model is difficult or impossible to learn [@Pong2020], as long as simulations of possible mechanisms are available.

>>>>

<!-- RL for behavioral ecology is not the same as RL for conservation -->
This paper does not set the precedent as the first application of RL to ecology.
There have been a number of studies applying RL to behavioral ecology, typically with multi-agent environments [@wang_reinforcement_2020, @frankenhuis_enriching_2019, @perolat_multi-agent_2017].
Yet, it is important to distinguish the aim of these behavioral studies from the aim of applying RL to conservation management. <!-- Compare using RL for conserv as prescriptive, behav eco as descriptive. We don't assume RL is the model. -->
In previous behavioral ecology studies, RL algorithms as a substitute for animal learning mechanisms [@wang_reinforcement_2020, @perolat_multi-agent_2017].
When applying deep RL to conservation management, we do not make the assumption that an RL algorithm learns analogously to how an animal learns.
We instead propose that RL be used as a tool to search for solutions to decision-making problems.

@@

<!-- Model free is great bc we don't know the true models -->
The rapidly expanding class of model-free RL algorithms is particularly appealing given the ubiquitous presence of model uncertainty in ecological dynamics.
Rarely do we know the underlying functional forms for ecological processes.
Methods which must first assume something about the structure or functional form of a process before estimating the corresponding parameter can only ever be as good as those structural assumptions.
Frequently, available ecological data are insufficient to distinguish between possible alternative models [@knape_are_2012], or the correct model may be non-identifiable with any amount of data.
Model-free RL approaches offer a powerful solution for this thorny issue.
Model-free algorithms have proven successful at learning effective policies even when the underlying model is difficult or impossible to learn [@Pong2020], as long as simulations of possible mechanisms are available.
